\papertitle

### 2021-03-11 source_separation/paper/paper.tex

		\subsection{Future Work}\label{sec:futurework}

		As we stated previously, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.

>>>>

		\subsection{Future Work}\label{sec:futurework}	
		As we stated previously, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.
